Using traffic analysis to identify The Second Generation Onion Router

### 2011-02-26 thesis/thesis.tex
Ram speed and 'capacity' instead of amount
Add in another appendix, clarify one of the answers
Rewrite abstract

Traditional attacks against anonymity providing systems aim to uncover the
identities of those involved. However, a more likely goal of attackers is to
block or degrade the network itself, discouraging participation and forcing
vulnerable users to communicate using less secure means. Since anonymous
networks operate on known protocols and employ strong encryption it is
difficult to distinguish them from regular traffic. This proposal describes a
method for identifying traffic belonging to anonymous networks by examining
their communication patterns.

@@

\begin{itemize*}
  \item CPU speed and number of cores
  \item RAM speed and amount
  \item Performance of integrated components, system bus etc.
  \item Hard disk size, access time and throughput
  \item Installed and running applications
  \item System configuration
\end{itemize*}

@@

@@

Don't know... yet.

@@

\lstinputlisting[language=ruby]{../experiment/simulation/manager/run_simulation.rb}

@@

\lstinputlisting[language=ruby]{../experiment/simulation/client/client.rb}

@@

\lstinputlisting[language=sh]{../experiment/simulation/tor/run_private_network.sh}

>>>>

Anonymous networks provide security for users by obfuscating messages with
encryption and hiding communications amongst cover traffic provided by other
network participants. In the academic literature, traditionally these networks
have been attacked with techniques that aim to uncover the identify of
participants. But the success of an anonymous network relies not only on it's
technical capabilities, but on adoption by a large enough user base to provide
adequate cover traffic. If anonymous network participants can be identified, the
users can be harassed, discouraging participation. Tor is an example of widely
used anonymous network which uses a form of Onion Routing to provide low latency
anonymous communications. This paper demonstrates that traffic from a simulated
Tor network can be distinguished from regular encrypted traffic, suggesting that
real world Tor users may be vulnerable to the same analysis.

@@

\begin{itemize*}
  \item CPU speed and number of cores
  \item RAM speed and capacity
  \item Performance of integrated components, system bus etc.
  \item Hard disk size, access time and throughput
  \item Installed and running applications
  \item System configuration
\end{itemize*}

@@

Yes, the classification algorithms trialled were all able to identify Tor traffic
with reasonable accuracy.

@@

@@

\label{manager-script}
\lstinputlisting[language=ruby]{../experiment/simulation/manager/run_simulation.rb}

@@

\label{client-script}
\lstinputlisting[language=ruby]{../experiment/simulation/client/client.rb}

\section{Generate Tor Network Script}

\label{generate-tor-network-script}
\lstinputlisting[language=sh]{../experiment/simulation/tor/make_private_network.sh}

@@

\label{run-tor-network-script}
\lstinputlisting[language=sh]{../experiment/simulation/tor/run_private_network.sh}
